\clearpage
\section{Summary}
\label{sec:tW_summary}

A search for new physics via top quark production in ee and \mumu final state has been performed using data recorded by CMS in 2016 from proton-proton collisions at $\sqrt{s} = 13$ TeV with 35.9 \fbinv\ integrated luminosity. The single top quark production in association with a W boson is probed for the first time together with the top quark pair production to find the new physics signatures. The results of the analysis have been also compared and combined with those of the analogous search in the $e\mu$ final state.
Observations are in agreement with standard model expectations. Limit interval at 68\% and 95\% confidence level on the effective couplings have been derived.
The results are interpreted to constrain the relevant effective couplings using a dedicated multivariate analysis. The observed $95\%$ CL limit bands on effective couplings are found to be [$-1.01$,0.70] for \CG, [$-0.41$,0.17]  for \CtG, [$-0.96$,5.74]  for \CtW and [$-3.82$,0.63] for \Cphiq. The corresponding expected limits are [$-1.07$,0.76] for \CG, [$-0.30$,0.28] for \CtG, [$-1.91$,6.70] for \CtW and [$-2.04$,1.63] for \Cphiq. For the FCNC effective couplings, the observed limits are [$-0.22$,0.22] and [$-0.46$,0.46] for \CuG and \CcG, respectively; the expected limits being [$-0.30$,0.30] and [$-0.65$,0.65]. The extracted values give the first experimental bound on the \CG coupling and  improve upon limits previously obtained at 8 TeV for \CtG. The limits obtained on the \CtW, \Cphiq, \CuG and \CcG couplings from the tW process are complementary to the limits from the single top t-channel process.

My personal contributions in this analysis: performing checks of distributions between data and simulations for different variables; working on the trigger scale factor study; estimating the various systematics uncertainties of the analysis; measuring the cross section of tW process for cross check; providing the final neural network spectra and the limits for different effective couplings. There is one publication for this analysis which is CMS-PAS-TOP-020.

This analysis is in publication by the CMS collaboration with one PAS document \cite{CMS-PAS-TOP-17-020} and it has also been submitted to journal.

